---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# add2impala

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/195213708.svg)](https://zenodo.org/badge/latestdoi/195213708)
<!-- badges: end -->

The goal of add2impala is to parse statistical metrics and encoding in SQL using R.
If you want to calculate KS statistic in R, free to try [rawKS](https://github.com/JiaxiangBU/rawKS).

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaxiangBU/add2impala")
```
## Example

```{r message=FALSE, warning=FALSE}
library(add2impala)
library(tidyverse)
```

### KS

```{r}
parse_ks_sql(verbose = 0, y_hat = "pred", y = "target", table = "opd.table")
parse_ks_sql(verbose = 1, y_hat = "pred", y = "target", table = "opd.table")
parse_ks_sql(verbose = 2, y_hat = "pred", y = "target", table = "opd.table")
```

The measurment explanation is 
[here](https://jiaxiangbu.github.io/learn_roc/ks_learning_notes.html#ks)
(Chinese).

### Regular expression

```{r}
inputs <- row.names(mtcars)
inputs %>% head
```

```{r}
# remotes::install_github("daranzolin/inferregex")
return_regex(inputs, verbose = "recommend")
return_regex(inputs, verbose = "all")
return_regex(inputs, verbose = "lazy")
```

### Rolling KS

```{r}
rolling_ks(
    y_hat = "pred",
    y = "target",
    table = "opd.test_pred_table",
    time_variable = "inserttime"
)
```



### cat2int

```{r eval=FALSE}
library(RODBC)
impala <- odbcConnect("Impala")
```

```{r eval=FALSE, include=FALSE}
cat2int(feature = "cyl", table = "opd.sqlsave_test_ljx") %>%
  write_rds("output/output_cat2int.rds")
```

```{r eval=F}
output_cat2int <- cat2int(feature = "cyl", table = "opd.sqlsave_test_ljx")
```

```{r include=FALSE}
output_cat2int <- read_rds("output/output_cat2int.rds")
```

```{r}
output_cat2int %>% cat
```

### paste_sql_result

可以方便把 SQL 反馈的结果，做成 markdown 格式，方便分享到 GitHub 或者 GitLab 上。

```{r eval=FALSE}
library(RODBC)
impala <- odbcConnect("Impala")
```


```{r eval=FALSE, include=FALSE}
paste_sql_result("describe opd.sqlsave_test_ljx") %>%
  write_rds("output/output_paste_sql_result1.rds")
```

```{r eval=F}
output_paste_sql_result1 <- paste_sql_result("describe opd.sqlsave_test_ljx")
```

```{r include=FALSE}
output_paste_sql_result1 <- read_rds("output/output_paste_sql_result1.rds")
```

```{r}
output_paste_sql_result1 %>% cat
```

```{r eval=FALSE, include=FALSE}
paste_sql_result("select * from opd.sqlsave_test_ljx limit 100") %>%
  write_rds("output/output_paste_sql_result2.rds")
```

```{r eval=F}
output_paste_sql_result2 <- paste_sql_result("select * from opd.sqlsave_test_ljx limit 100")
```

```{r include=FALSE}
output_paste_sql_result2 <- read_rds("output/output_paste_sql_result2.rds")
```

```{r}
output_paste_sql_result2 %>% cat
```

***

`r add2pkg::add_disclaimer()`
